Software Citation Principles

### 2016-03-21 sc-principles/software-citation-principles.tex
A sub-section
More sub-sections
A comment about professional societies

\textbf{General community/non domain-specific activities}

@@

\textbf{Domain-specific community activities}

One approach to increasing the `citability' of software is to encourage the
submission of papers in standard journals describing a piece of research
software. While some journals (e.g., F1000Research) have traditionally accepted
software submissions, the American Astronomical Society (AAS) have recently
announced they will accept software papers in their journals
\cite{aas-sofware-papers}.

@@

\asnote{Perhaps we should say something here about the potential importance of professional societies and their role in effecting changes in community practice?}

@@

\textbf{Existing principles}

>>>>

\subsection{General community/non domain-specific activities}

@@

\subsection{Domain-specific community activities}

One approach to increasing the `citability' of software is to encourage the
submission of papers in standard journals describing a piece of research
software. While some journals (e.g., F1000Research) have traditionally accepted
software submissions, the American Astronomical Society (AAS) have recently
announced they will accept software papers in their journals
\cite{aas-sofware-papers}. As the publishers of journals and convenors of domain-specific conferences the authors note the potential importance of professional societies in effecting changes in community practice.

@@

@@

\subsection{Existing principles}
